---
format:
  html:
    subtitle: | 
      How we have allocated data from sources to the domains and themes of
      the Index's conceptual framework and data model.
source_document: https://index.bsg.ox.ac.uk/posts/source_alignment/
order: 108
---

# Alignment of sources to the Index's conceptual framework {#sec-source_alignment}

```{r}
#| label: setup
#| echo: false

source("R/out_table.R")

source_meta <- readr::read_csv(
  file.path("data", "source_summary.csv"), show_col_types = FALSE
)

metrics_meta <- readr::read_csv(
  file.path("data", "metrics_summary.csv"), show_col_types = FALSE
)

bipa_structure <- readr::read_csv(
  file.path("data", "bipa2024_data_structure.csv"), show_col_types = FALSE
)

metrics_summary <- function(theme, df = metrics_meta) {
  df |>
    dplyr::filter(floor(structure_id/100) == theme/100) |>
    dplyr::arrange(structure_id) |>
    dplyr::select(
      indicator, metric_label, data_source, source_variable, collection_type,
      ref_year, transformation, n_countries
    ) |>
    gt::gt(groupname_col = "indicator", row_group_as_column = TRUE) |>
    gt::tab_stubhead("Indicator") |>
    gt::cols_label(
      indicator ~ "Indicator",
      metric_label ~ "Metric",
      data_source ~ "Source",
      source_variable ~ "Source variable",
      collection_type ~ "Type of collection",
      ref_year ~ "Year(s)",
      transformation ~ "Data transformation",
      n_countries ~ "Number of countries"
    ) |>
    gt::cols_align(align = "right", columns = c(ref_year, n_countries)) |>
    gt::cols_width(
      indicator ~ gt::pct(10),
      metric_label ~ gt::pct(10),
      data_source ~ gt::pct(6),
      source_variable ~ gt::pct(39),
      collection_type ~ gt::pct(10),
      ref_year ~ gt::pct(6),
      transformation ~ gt::pct(12),
      n_countries ~ gt::pct(7)
    ) |>
    out_table(width = 1000)
    
}

```

In order to calculate the Index, and its components, the source data needs to
be aligned against our conceptual framework, in. doing so the following approach
was followed:

- To ensure simplicity of the methodology for calculating the Index, variables
from the source data were allocated to only one theme.
- When selecting the theme to allocate a variable to, maximising coverage of
the conceptual framework has been prioritised.
- Variables measuring similar concepts are grouped together to define the
indicators within that theme.

This section describes the relationship of source data to the Index’s conceptual
framework and data model. For each theme, a table details the indicators and
variables that make up the theme, it also lists any transformation of the
variables and metadata about the variable/source (reference year(s), number of
countries covered, type of data collection).

To enable effective comparison, all source data is translated to a 0-to-1 scale,
in addition to scaling some data undergoes a transformation (e.g. data where
higher scores relate to poorer performance are inverted) before it is scaled,
@sec-rescaling_transformation describes the different transformation processes
outlined in the metrics tables.

The type of data collection used for each of the sources have been coded into
one of nine types, which can be grouped into three broad groupings (quantitative
data, assessments, and opinion measures):

- Quantitative data
    - Administrative data – published data drawn from administrative systems
      (e.g. data submitted by tax agencies to the International Survey of
      Revenue Administration).
    - Official statistics – published data drawn from official statistics (e.g.
      official statistics data collated by the International Labor Organization).
    - Statistical analysis – statistical analysis conducted on government
      data/publications (e.g. the analysis of policy documents used by the
      PARIS21 Statistical Capability Monitor).
- Assessments
    - Expert assessment – external objective assessment of government practices
    (e.g. assessment and analysis of open data published by governments by
    civil society researchers for the Global Data Barometer).
    - Government self-assessment – responses by government officials to a survey
      (e.g. responses by officials to the World Bank survey that is used to
      calculate the GovTech Maturity Index).
- Opinion measures
    - Business opinion – responses by businesses to an opinion survey (e.g.
      responses by businesses to the World Bank survey used to collect
      information for the Logistics Performance Index).
    - Expert opinion – responses by experts to an opinion survey (e.g.
      responses by academics/civil society experts to the Quality of Government
      Expert Survey), or assessments by experts that provide a rating (e.g.
      academic/civil society expert ratings used to produce in the Bertelsmann
      Transformation Index).
    - General public opinion – responses by the general public to an opinion
      survey (e.g. responses by members of the public to the survey used to
      calculate the Global Corruption Barometer).
    - Combined expert and public option – the combination of responses from
      surveys of experts and the general public (e.g. the combination of a
      survey of legal professionals and a general public opinion survey used
      in the production of the Rule of Law Index).


:::{.landscape}

```{r}
#| label: tbl-source_ref
#| tbl-cap: > 
#|   Data sources used in the Blavatnik Index of Public Administration 2024

source_meta |>
  gt::gt() |>
  gt::cols_hide("source_id") |>
  gt::cols_label(
    source_name = "Data source",
    publisher = "Publisher",
    collection_type = "Type of data collection",
    ref_year = "Reference year(s)",
    website = "Website"
  ) |>
  gt::fmt_url("website") |>
  gt::cols_width(
    source_name ~ gt::pct(25),
    publisher ~ gt::pct(15),
    collection_type ~ gt::pct(12),
    ref_year ~ gt::pct(8),
    website ~ gt::pct(40)
  ) |>
  out_table(width = 1000)

```

:::

## Strategy and Leadership domain

The strategy and leadership domain has five themes: strategic capacity;
cross-government collaboration; openness and communications; integrity; and,
innovation. Of these, all but cross-government collaboration can be measured
from sources with global coverage.

### Strategic capacity

There are two sources for the strategic capacity theme: the Bertelsmann
Transformation Index (BTI) and the Sustainable Governance Indicators (SGI). Four
measures are extracted from these sources and used to estimate one indicator:
prioritisation.

The prioritisation indicator measures the extent to which governments can set
priorities/strategies. It is estimated by two measures from the SGI measuring
the influence of strategic planning units and the strategic appraisal capability
of the centre of government, these are complemented by the BTI measures on the
setting of strategic priorities and the efficiency of resource allocation.

A further three measures were identified from OECD/EU only sources, these could
be used to estimate a second indicator on institutional adaptation.

- Metrics table: @tbl-strled_cap
- Framework definition: @sec-strategic-capacity-theme

### Cross-government collaboration

Four measures from the Sustainable Governance Indicators were identified
as potential metrics for the collaboration theme, which could be used to
estimate two indicators: collaboration in policy development, and international
collaboration; however, there were no appropriate measures in the Bertelsmann
Transformation Index that these could be matched with. Therefore, the
collaboration theme is not measured in the global version of the index.

- Metrics table: *not available*
- Framework definition: @sec-xgov-collaboration-theme

### Openness and communications

There are four sources for the openness and communications theme: the Bertelsmann
Transformation Index (BTI), the GovTech Maturity Index, the Rule of Law Index,
and the Sustainable Governance Indicators (SGI). Seven measures are extracted
from these sources and are used to estimate three indicators: right to
information; open government; and, engagement and feedback.

The right to information indicator assesses the extent to which non-government
actors/members of the public can obtain/request access to official information.
It is estimated from the ROLI measure on right to information.

The open government indicator assesses the extent to which non-government
actors/members of the public can access laws/regulations and the extent to
which governments make information proactively available to the public. It is
estimated from the ROLI measure on publicized laws and government data and a
measure extracted from the GTMI on the existence of portals for open government
initiatives and open data.

The engagement and feedback indicator assesses the extent and nature of
government consultation in the development of policies and regulations and
whether service users can provide feedback about their experience of public
services. It is estimated from a measure from the SGI matched with a measure
from the BTI, both measuring consultation with non-state actors, the ROLI
measure on complaint mechanisms and a measure extracted from the GTMI on digital
methods for public participation.

A further 9 measures were identified from OECD/EU only sources, these would
add further depth to the three global indicators as well as estimate a fourth
indicator around public communications.

- Metrics table: @tbl-strled_opn
- Framework definition: @sec-openness-communications-theme

### Integrity

There are six sources for the integrity theme: the Bertelsmann
Transformation Index (BTI), the Global Corruption Barometer (GCB), the Global
Data Barometer, the Quality of Government Expert Survey (QOG), the Rule of Law
Index (ROLI), and the Varieties of Democracy Dataset (VDEM). 10 measures are
extracted from these sources and are used to estimate four indicators: impartial
behaviour; corruption; sanctions; and, integrity data.

The impartial behaviour indicator measures the degree of impartiality in the
operation of public administrations, i.e. the extent to which politicians
interfere with day-to-day administrative practice and delivery of public
services. It is estimated by the QOG measures on whether officials act with
impartiality and political interference in bureaucratic decision making, the
ROLI measure on whether due process is respected in administrative proceedings,
and the VDEM measure on whether public officials are impartial in the
performance of their duties.

The corruption indicator measures the extent to which officials are not involved
in corruption/corrupt practices. It is estimated by the GCB measure on public
perception of the extent of officials involved in corruption, and the VDEM
measures on whether public officials grant favours in return for a bribe and
whether officials misuse or embezzle public funds/resources.

The sanctions indicator measures the extent to which officials found to engage
in misconduct are sanctioned for their misbehaviour. It is estimated by the BTI
measure on the extent to which officials are prosecuted and the ROLI measure on
the extent to which officials are sanctioned.

The integrity data indicator measures the availability of data published
by government relating to public integrity (e.g. registers of interests,
gifts, meetings etc). It is estimated by the GDB’s measure on integrity data
availability.

A further five metrics were identified in OECD/EU only sources, these would
provide estimates for two further indicators: the existence of an integrity
framework; and, practices for managing conflicts of interest.

- Metrics table: @tbl-strled_int
- Framework definition: @sec-integrity-theme

### Innovation

There are three sources for the innovation theme: the Bertelsmann Transformation
Index (BTI), the GovTech Maturity Index (GTMI), and the International Survey of
Revenue Administration (ISORA). Three measures are extracted from these sources
to measure one indicator: innovative approach.

The innovative approach indicator measures the extent to which governments
are adopting or supporting innovative practices in the development of policy
or delivery of public services. It is estimated by the BTI measure rating how
innovative and flexible governments are overall, data extracted from the GTMI
relating to the support for innovation (with a focus on digital services/new
technology), and the use of innovative practices by the tax administration.

- Metrics table: @tbl-strled_inv
- Framework definition: @sec-innovation-theme

## Public Policy domain

The public policy domain has five themes: policy making; financial management;
regulation; crisis and risk management; and, use of data and statistics. All five
themes in the public policy domain can be measured from global sources.

### Policymaking

There are two sources for the policymaking theme: the Bertelsmann
Transformation Index (BTI) and the Sustainable Governance Indicators (SGI).
Two measures are extracted from these sources to estimate one indicator: policy
coordination.

The policy coordination indicator measures the extent to which government
design coordinated policies. It is estimated by the SGI measure on the
ministerial/cabinet coordination matched with the BTI measure on coordinating
conflicting objectives.

A further four measures were identified in OECD/EU only sources, these
would provide estimates of two additional indicators: policy expertise; and, policy
evaluation.

- Metrics table: @tbl-pubpol_pol
- Framework definition: @sec-policymaking-theme

### Financial management

Three measures were identified from the Open Budget Survey relating to the
transparency of budget documents, budget consultation practices and the
transparency of budget oversight, as well as one measure from the Global
Data Barometer relating to the availability of public finance data. However,
on further review it was decided not to include these measures owing to the
potential for misinterpretation of the results. These measures focus principally
on the transparency of fiscal information provided by the government, while
this is an important component it does not measure important internal practices
such as the use of spending reviews, cost benefit analysis, spend controls
and authorisation processes, internal record keeping/management information or
internal audit processes. Moreover, several of the countries that score well in
these transparency measures have well documented instances of corruption, and/or
make use of national security legislation or extrabudgetary measures to hide
some degree of their public expenditure.

More traditional measures of public financial management use output/outcome
indicators such as the debt to GDP ratio, tax revenue as a share of GDP, public
expenditure as a share of GDP, yields on government bonds. While good practices
in the management of the public finances is likely an important factor in these
indicators, they are much more likely to be influenced by wider economic factors
and specific political decisions, meaning that these types of measures are out
of scope.

In keeping with our principle for a simple and transparency methodology, since
we have been unable to identify a simple approach to accounting for either
corruption or the hiding of public expenditure it was decided not to include
measures on financial management in the calculation of the Index at this stage.

- Metrics table: *not available*
- Framework definition: @sec-financial-management-theme

### Regulation

There is one source for the regulation theme: the Rule of Law Index (ROLI).
Two measures are extracted from this source to estimate a single indicator:
regulatory enforcement.

The regulatory enforcement indicator measures the extent to which regulations
are enforced effectively and properly. It is estimated from the ROLI measures
on the effective enforcement of regulations and the enforcement of regulation
without improper influence.

A further six measures were identified in OECD/EU only sources, one measure
would add to the existing metrics estimating the regulatory enforcement
indicator while the others would estimate an additional indicator on the use of
regulatory impact assessment.

- Metrics table: @tbl-pubpol_reg
- Framework definition: @sec-regulation-theme

### Crisis and risk management

There are two sources for the crisis and risk management theme: the Global
Cybersecurity Index (GCI) and the Sendai Framework Monitor (SFM). Six measures
are extracted from these sources to estimate two indicators: natural hazards;
and, cybersecurity.

The natural hazards indicator measures the extent to which governments have
strategies to respond to natural hazard disasters. It is estimated from the SFM
measure on disaster risk reduction strategies.

The cybersecurity indicator measures the extent to which governments have
strategies and practices in places to handle cybersecurity risks. It is
estimated from the five pillars of the GCI: capacity building measures,
cooperative measures, legal measures, organisational measures, and technical
measures.

- Metrics table: @tbl-pubpol_crm
- Framework definition: @sec-crisis-risk-theme

### Use of data and statistics

There are three sources for the use of data and statistics theme: the Global
Data Barometer (GDB), the Open Data Inventory (ODIN) and the PARIS21 Statistical
Capacity Monitor (PARIS21). 13 measures are extracted from these sources to
estimate four indicators: data capability; data availability; data coverage; and
data re-use.

The data capability indicator measures the extent of government support for data
skills and capabilities, and governance policies for data and statistics. It is
estimated from the GDB measures on data governance and data capability.

The data availability indicator measures the availability of official statistics
and other open data published by government. It is estimated from the GDB
measures on the availability of company data, land data, health data and climate
data, and the ODIN measures on the openness of economic statistics, social
statistics and environmental statistics.

The data coverage indicator measures the extent of indicators and disaggregation
published and availability of time-series data. It is estimated from the ODIN
measures on the coverage of economic, social and environmental statistics.

The data re-use indicator measures the extent to which data and statistics are
used/re-used. It is estimated from the PARIS21 measure on the use of statistics
in policy documents.

A further three measures were identified in OECD/EU only sources, these would
provide further metrics for the data availability and data re-use indicators.

- Metrics table: @tbl-pubpol_dat
- Framework definition: @sec-use-of-data-theme

## National Delivery domain

The national delivery domain has five themes: system oversight, digital
services, tax administration, border services, and social security. Of these,
all but social security can be measured from global sources.

### System oversight

There are two sources for the system oversight theme: the Bertelsmann
Transformation Index (BTI) and the Sustainable Governance Indicators (SGI).
Two measures are extracted from these sources to estimate one indicator: policy
implementation.

The policy implementation indicator measures the extent to which governments are
able to achieve objectives. It is estimated by the SGI measure on the extent to
which government can achieve its policy objectives matched with the BTI measure
on whether the government can implement its policies.

A further six measures were identified in OECD/EU only sources, these would
provide estimates for two additional indicators: policy monitoring and
subnational relations.

- Metrics table: @tbl-natdel_sys
- Framework definition: @sec-system-oversight-theme

### Digital services

There is one source for the digital service theme: the GovTech Maturity Index
(GTMI). Three measures are extracted from this source, each estimating one
indicator: digital strategy and policies; infrastructure; and, digital public
services.

The digital strategy and policy indicator measures the existence of strategies,
policies and practices that support the government’s approach to digital
services. It is estimated from data extracted from the GTMI on digital
strategies and policies.

The infrastructure indicator measures the existence of technologies that support
the delivery of digital services. It is estimated from data extracted from the
GTMI on back-end technologies and infrastructure.

The digital public services indicator measures the extent of digital services
for end-users. It is estimated from the data extracted from the GTMI on the
existence of service portals, e-payment services and use of digital signature
technologies.

A further 14 measures were identified in OECD/EU only sources, these would
provide further metrics to estimate the digital strategy and policy, the
infrastructure, and the digital public services indicators, it would also
provide metrics to estimate an additional indicator on user-centric service
design and development.

- Metrics table: @tbl-natdel_dig
- Framework definition: @sec-digital-services-theme

### Tax administration

There are two sources for the tax administration theme: the Doing Business
report (DB), and the International Survey of Revenue Administration (ISORA).
12 metrics are extracted from these sources to estimate three indicators: tax
agency administration; tax compliance; and, digital tax services.

The tax agency administration indicator measures the administrative functioning
of the tax agency. It is estimated by the ISORA measures on administrative costs
(as a percent of net revenue) and the turnover of tax agency staff.

The tax compliance indicator measures the compliance of taxpayers with their
obligations and the effectiveness of the tax agency in enforcing compliance.
It is estimated by the ISORA measures on the rate of taxes filed on time (for
both corporate and personal taxes), the rate of taxes paid on time (for both
corporate and personal taxes), and tax debt (as a percent of net revenue), it is
also estimated by the DB measure on the annual time businesses must take to file
tax returns/declarations.

The digital tax services indicator measures the use of digital methods for
interacting with the tax agency. It is estimated from the ISORA measures on
the proportion of taxes filed electronically (for both corporate and personal
taxes), the proportion of taxes paid electronically, and the proportion of
service contacts that occur via digital channels.

- Metrics table: @tbl-natdel_tax
- Framework definition: @sec-tax-administration-theme

### Border services

There is one source for the border services theme: the Logistics Performance
Index (LPI). One measure is extracted from this source to estimate a single
indicator: customs processes.

The customs processes indicator measures the ease with which goods can be
shipped across international borders. It is estimated by the LPI measure on the
efficiency of customs processes.

- Metrics table: @tbl-natdel_brd
- Framework definition: @sec-border-services-theme

### Social security

The GovTech Maturity Index provides data on the existence of portals for social
security insurance and job searches. These are included in the measurement of
the digital public services indicator in the digital services theme. No other
measures of the functioning and practice of national-level social security
services have been identified.

- Metrics table: *not available*
- Framework definition: @sec-social-security-theme

## People and Processes domain

The people and processes domain has five themes: employee engagement; diversity &
inclusion; HR management; procurement; and, technology and workplaces. Of these,
only diversity and inclusion, HR management and procurement can be measured from
global sources.

### Employee engagement

Measures relating to learning and development practices were identified in one
OECD/EU only source. There were no measures identified with extensive country
coverage that would allow for estimation of an indicator relating to employee
engagement in a global version of the index.

- Metrics table: *not available*
- Framework definition: @sec-employee-engagement-theme

### Diversity and inclusion metrics

There are four sources for the diversity and inclusion theme: the EIGE Gender
Statistics Database (EIGE), the International Labor Organization (ILO), the
International Survey of Revenue Administration (ISORA), and the Varieties of
Democracy Dataset (VDEM). Ten measures are extracted from these sources to
estimate three indicators: inclusive recruitment; gender diversity (all staff);
and, gender diversity (management).

The inclusive recruitment indicator measures the extent to which individuals
with different characteristics or backgrounds are able to apply for government
jobs. It is estimated from the VDEM measures on whether state jobs are open
to those regardless of their gender, their rural or urban location, their
socio-economic position, their social group (e.g. ethnic or religious group), or
their political group.

The gender diversity (all staff) indicator measures the extent to which gender
parity is achieved across the employee base. It is estimated from data extracted
from the ILO on women in public administration employment, the ISORA measure on
the proportion of all those working at the tax agency that are women, and data
extracted from the ILO comparing the hourly earnings of men and women in the
public sector.

The gender diversity (management) indicator measures the extent to which gender
parity is achieved at management/senior levels of the public sector. It is
estimated from data extracted from the EIGE and ILO on women in management
positions, and the ISORA measure on the proportion of senior officials working
at the tax agency that are women.

An additional metric was identified from OECD/EU only sources that would provide
an additional metrics for the estimate of inclusive recruitment.

- Metrics table: @tbl-pplprc_inc
- Framework definition: @sec-diversity-inclusion-theme

### HR management

There are two sources for the HR management theme: the Quality of Government
Expert Survey (QOG) and the Varieties of Democracy Dataset (VDEM). Five measures
are extracted from these sources to estimate two indicators: recruitment regime;
and, meritocratic appointment.

The recruitment regime indicator measures the openness and security of
recruitment to public administration jobs. It is estimated by the QOG measures
on hierarchy levels subject to open recruitment and on the security of tenure
enjoyed by public employees.

The meritocratic appointment indicator measures the extent to which appointment
decisions in the public administration are based on merit and not on patronage.
It is estimated by the QOG measures on recruitment by merit and patronage, and
the VDEM measure on recruitment not by patronage.

- Metrics table: @tbl-pplprc_hrm
- Framework definition: @sec-hr-management-theme

### Procurement

There is one source for the procurement theme: the Global Data Barometer (GDB).
One measure is extracted from this source to estimate a single indicator:
procurement data.

The procurement data indicator measures the availability of data relating to
public procurement tenders and contracts. It is estimated from the GDB measure
on procurement data.

- Metrics table: @tbl-pplprc_pro
- Framework definition: @sec-procurement-theme

### Technology and workplaces metrics

There is one source for the technology and workplaces theme: the GovTech
Maturity Index (GTMI). One measure is extracted from this source to estimate a
single indicator: administrative IT systems.

The administrative IT systems indicator measures the existence of management
information systems for administrative activities. It is estimated based on data
extracted from the GTMI on the existence and nature of MI systems for public
finances, HR management, payroll services and public procurement.

- Metrics table: @tbl-pplprc_twk
- Framework definition: @sec-technology-workplaces-theme

## Metrics definition tables

The following tables provide metadata about the metrics for each of the 4
domains and 16 themes that comprise the Blavatnik Index of Public
Administration 2024. For each metric the table provides a label, the data
source reference, the original variable label in the data source, the type
of collection used by the data source, the reference year(s) of the data used
by the Blavatnik Index, any transformation applied to the data, and the number
of countries for which there is data available.

:::{.landscape}

```{r}
#| label: tbl-strled_cap
#| tbl-cap: Metrics for the strategic capacity theme
metrics_summary(10100)
```

:::

:::{.landscape}

```{r}
#| label: tbl-strled_opn
#| tbl-cap: Metrics for the openness and communications theme
metrics_summary(10300)
```

:::

:::{.landscape}

```{r}
#| label: tbl-strled_int
#| tbl-cap: Metrics for the integrity theme
metrics_summary(10400)
```

:::

:::{.landscape}

```{r}
#| label: tbl-strled_inv
#| tbl-cap: Metrics for the innovation theme
metrics_summary(10500)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pubpol_pol
#| tbl-cap: Metrics for the policmaking theme
metrics_summary(20100)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pubpol_reg
#| tbl-cap: Metrics for the regulation theme
metrics_summary(20300)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pubpol_crm
#| tbl-cap: Metrics for the crisis and risk management
metrics_summary(20400)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pubpol_dat
#| tbl-cap: Metrics for the use of data and statistics theme
metrics_summary(20500)
```

:::

:::{.landscape}

```{r}
#| label: tbl-natdel_sys
#| tbl-cap: Metrics for the system oversight theme
metrics_summary(30100)
```

:::

:::{.landscape}

```{r}
#| label: tbl-natdel_dig
#| tbl-cap: Metrics for the digital services theme
metrics_summary(30200)
```

:::

:::{.landscape}

```{r}
#| label: tbl-natdel_tax
#| tbl-cap: Metrics for the tax administration theme
metrics_summary(30300)
```

:::

:::{.landscape}

```{r}
#| label: tbl-natdel_brd
#| tbl-cap: Metrics for the border services theme
metrics_summary(30400)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pplprc_inc
#| tbl-cap: Metrics for the diversity and inclusion theme
metrics_summary(40200)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pplprc_hrm
#| tbl-cap: Metrics for the HR management theme
metrics_summary(40300)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pplprc_pro
#| tbl-cap: Metrics for the procurement theme
metrics_summary(40400)
```

:::

:::{.landscape}

```{r}
#| label: tbl-pplprc_twk
#| tbl-cap: Metrics for the technology and workplaces theme
metrics_summary(40500)
```

:::
