---
format:
  html:
    subtitle: | 
      How we assess country data coverage and use this to determine the
      countries in the final Index.
    fig-width: 7
    fig-height: 7
  pdf:
    fig-width: 6
    fig-height: 6
source_document: https://index.bsg.ox.ac.uk/posts/country_selection/
params:
  math: true
order: 109
---

# Data coverage and country selection {#sec-country_selection}

```{r}
#| label: setup
#| echo: false
#| include: false

library(ggplot2)
source("R/out_table.R")

bipa_dqc <- readr::read_rds(file.path("data", "bipa2024_dqc_full.rds"))
bipa_results <- readr::read_csv(file.path("data", "bipa2024_all_data.csv"))
cc_ref <- readr::read_csv(file.path("data", "entity_codes.csv"))
cc_geo <- readr::read_csv(file.path("data", "entity_georegions.csv"))
cc_wb <- readr::read_csv(file.path("data", "entity_wb_classification23.csv"))
cc_wdi <- readr::read_csv(file.path("data", "wb_wdi_2024.csv"))

cc_pop <- cc_wdi |>
  dplyr::filter(variable == "wb_pop_total") |>
  dplyr::filter(ref_year == max(ref_year), .by = cc_iso3c) |>
  dplyr::mutate(
    pop_group = dplyr::case_when(
      value < 5e6 ~ "(1) Less than 5 million",
      value < 10e6 ~ "(2) 5 million to 10 million",
      value < 25e6 ~ "(3) 10 million to 25 million",
      value < 50e6 ~ "(4) 25 million to 50 million",
      value >= 25e6 ~ "(5) 50 million or greater",
    )
  ) |>
  dplyr::select(cc_iso3c, pop_value = value, pop_group)

cc_meta <- cc_ref |>
  dplyr::left_join(cc_geo, by = "cc_iso3c") |>
  dplyr::left_join(cc_wb, by = "cc_iso3c") |>
  dplyr::left_join(cc_pop, by = "cc_iso3c") |>
  dplyr::filter(cc_iso3c != "ATA")
```

Any analytical exercise needs to carefully consider the quality of its data,
this is particularly important when combining data from different data sources.
This section explores country data quality, in particular data availability for
countries, to determine inclusion in the Index’s calculations.

Of the `r nrow(bipa_dqc$dq_data)` countries and territories which have data for
at least one of the 86 metrics used for the global index, only one country
(Mexico) has data for all 86 metrics, as a result an approach is needed to
consider a country’s data coverage for determining its inclusion in the
calculation of the Index.

A simple approach for determining coverage would be to consider simply the total
number of metrics a country has data for ($m_c$) as a proportion of the total
number of possible metrics ($M$).

$$
p_m = \frac{m_c}{M}
$$

However, this approach does not consider how a country’s data is spread across
the structure of our conceptual framework and data model – a country with a
higher proportion of metrics concentrated in fewer themes would do better on
this simple measure than a country with a lower proportion of metrics spread
across more themes. As described in section 6 missing data is not subject
to imputation, good coverage of the data model is therefore an important
consideration to ensure that the implicit estimate of missing data will come
from “sibling” components in the data model.

Based on the chi-square test we have developed an algorithm for assessing a
country’s data availability. This algorithm assesses both the volume of metrics
a country has as well as the spread of that data over the data model. For
each country-theme combination, an information quotient is calculated as the
square of the difference between the total number of metrics a country has for
that theme ($m_{t,c}$) and the number of indicators a country has for that
theme ($i_{t,c}$) divided by the overall number of indicators in that theme
($i_t$). The overall data coverage score for a country ($Q_c$) is
calculated as the sum of these country-theme information quotients adjusted for
overall coverage across the themes, calculated as the number of themes a
country has data for ($t_c$) divided by overall number of themes ($T$).


$$
    Q_c= \displaystyle\sum_{t=1}^{t_c} \frac{(m_{t,c}-i_{t,c}+1)^2}{i_t}
$$

Having calculated the data coverage algorithm, we can set criteria to determine
inclusion in the calculation of the Index and its components. Two principal
criteria were selected :

- The overall data coverage score ($Q_c$) is greater than or equal to half its
  theoretical maximum value (i.e. the score a country would achieve if it has
  data for all metrics). The maximum data coverage score is
  `r scales::number(bipa_dqc$dq_ref$x_a, 0.01)`, the threshold value is
  therefore `r scales::number(bipa_dqc$threshold_q, 0.01)`.
- While the overall score does take into consideration the number of metrics,
  the overall percentage of metrics a country has ($p_m$) is also retained as
  a secondary threshold. It was decided to only include countries and
  territories with at least 2/3rds of overall metrics.

These criteria give rise to a selection of `r bipa_dqc$n_countries` countries
and territories[^hkg].

The inclusion criteria provide a binary state of whether countries are included
or not however we can also devise a grading scheme using the same measures
to determine inclusion to give a better sense of an individual country’s data
coverage. For countries and territories above thresholds for inclusion in the
Index the lower quartile, median and upper quartile of their data coverage score
and percentage of metrics are used to define the boundaries for the first four
grades (A-D); for countries and territories below the thresholds for inclusion
in the Index the median of their data coverage score and percentage of metrics
is used to define the boundary between the fifth and sixth grade (E-F). The
following tables provide summarises of data coverage metrics: 
@tbl-dq_grades by grade; @tbl-dq_by_groups by regional, economic and
population groupings. Full data coverage metrics for all countries and
territories are provided in @tbl-dq_included and @tbl-dq_not_included.

```{r}
#| label: tbl-dq_grades
#| tbl-cap: Summary of data coverage metrics by grade

dq_grade_summary <- tibble::tibble(
  grade = names(bipa_dqc$dq_grade_thresholds$q_thresholds),
  x_a = bipa_dqc$dq_grade_thresholds$q_thresholds,
  p_m = bipa_dqc$dq_grade_thresholds$m_thresholds
) |>
  dplyr::arrange(grade) |>
  dplyr::full_join(
    bipa_dqc$dq_data |>
      dplyr::mutate(
        dq_grade = dplyr::if_else(cc_iso3c == "HKG", "E", dq_grade)
      ) |>
      dplyr::count(grade = dq_grade),
    by = "grade"
  ) |>
  dplyr::add_row(
    grade = "Ungraded (no data)",
    n = nrow(cc_ref) - nrow(bipa_dqc$dq_data)
  ) |>
  dplyr::mutate(
    across(c(x_a, p_m), ~ tidyr::replace_na(.x, 0)),
    criteria_marker = dplyr::case_when(
      grade %in% LETTERS[1:5] ~ "≥",
      grade == "F" ~ ">",
      TRUE ~ "="
    ),
    criteria = glue::glue(
      "Q<sub>c</sub> {criteria_marker} {scales::number(x_a, 0.01)}, ",
      "p<sub>m</sub> {criteria_marker} {scales::percent(p_m, 0.01)}",
      sep = " "
    ),
    criteria = gsub("0.00", "0", criteria),
    group = dplyr::if_else(
      grade %in% LETTERS[1:4],
      "Countries included in the index",
      "Countries and territories not included in the index"
    )
  ) |>
  dplyr::select(group, grade, criteria, n)

gt::gt(dq_grade_summary, groupname_col = "group") |>
  gt::fmt_markdown(criteria) |>
  gt::cols_label(
    grade = "Data coverage grade",
    criteria = "Data coverage thresholds",
    n = "Number of countries"
  ) |>
  gt::tab_footnote(
    footnote = gt::md(paste(
      "Q<sub>c</sub> is the data coverage score, p<sub>m</sub> is the percent",
      "of total metrics"
    )),
    locations = gt::cells_column_labels(columns = criteria)
  ) |>
  gt::tab_footnote(
    footnote = gt::md(paste(
      "Hong Kong included in many of the source datasets used by the Index and",
      "has Q<sub>c</sub> and p<sub>m</sub> scores equivalent to grade D. As a",
      "territory of China, Hong Kong is not included in the Blavatnik Index,",
      "therefore it has been included in this summary table in the total number",
      "of countries for grade E."
    )),
    locations = gt::cells_body(columns = grade, rows = grade == "E")
  ) |>
  {
    \(x) {
      if (knitr::is_latex_output()) {
        x$`_data`$criteria <- gsub("≥", ">=", x$`_data`$criteria, perl = TRUE)
        x$`_data`$criteria <- gsub(
          "</?sub>",
          "",
          x$`_data`$criteria,
          perl = TRUE
        )
        x$`_footnotes`$footnotes <- gsub(
          "</?sub>",
          "",
          x$`_footnotes`$footnotes,
          perl = TRUE
        )
        return(x)
      } else {
        return(x)
      }
    }
  }() |>
  out_table()

```

```{r}
#| label: tbl-dq_by_groups
#| tbl-cap: Summary of country coverage by groupings

dq_data_groups <- bipa_dqc$dq_data |>
  dplyr::full_join(cc_meta, by = "cc_iso3c") |>
  dplyr::mutate(
    sum_group = dplyr::case_when(
      included ~ "all_included",
      cc_status == "UN member" ~ "not1_un",
      TRUE ~ "not2_oth"
    )
  )

dq_cc_groups <- dplyr::bind_rows(
  dq_data_groups |>
    dplyr::summarise(
      agg_group = "0_all",
      agg_cat = "All countries and territories",
      n = dplyr::n(),
      .by = sum_group
    ),
  dq_data_groups |>
    dplyr::summarise(
      agg_group = "1_region",
      n = dplyr::n(),
      .by = c(bipa_region, sum_group)
    ) |>
    dplyr::arrange(bipa_region) |>
    dplyr::rename(agg_cat = bipa_region),
  dq_data_groups |>
    dplyr::summarise(
      agg_group = "2_income",
      n = dplyr::n(),
      .by = c(income_group, sum_group)
    ) |>
    dplyr::arrange(income_group) |>
    dplyr::rename(agg_cat = income_group),
  dq_data_groups |>
    dplyr::summarise(
      agg_group = "3_population",
      n = dplyr::n(),
      .by = c(pop_group, sum_group)
    ) |>
    dplyr::arrange(pop_group) |>
    dplyr::mutate(pop_group = gsub("^\\(\\d\\) ", "", pop_group)) |>
    dplyr::rename(agg_cat = pop_group)
) |>
  tidyr::pivot_wider(names_from = sum_group, values_from = n) |>
  dplyr::mutate(
    agg_cat = dplyr::case_when(
      is.na(agg_cat) & agg_group == "2_income" ~
        "No World Bank income classification",
      is.na(agg_cat) & agg_group == "3_population" ~ "No population data",
      TRUE ~ agg_cat
    ),
    agg_cat = forcats::as_factor(agg_cat)
  ) |>
  dplyr::select(agg_group, agg_cat, all_included, not1_un, not2_oth)

dq_cc_groups |>
  gt::gt(rowname_col = "agg_cat") |>
  gt::tab_row_group(
    label = "",
    rows = agg_group == "0_all",
    id = "0_all"
  ) |>
  gt::tab_row_group(
    label = "Geographic region",
    rows = agg_group == "1_region",
    id = "1_region"
  ) |>
  gt::tab_row_group(
    label = "Income group (World Bank, 2023)",
    rows = agg_group == "2_income",
    id = "2_income"
  ) |>
  gt::tab_row_group(
    label = "Population size (World Bank, 2022)",
    rows = agg_group == "3_population",
    id = "3_population"
  ) |>
  gt::row_group_order(c("0_all", "1_region", "2_income", "3_population")) |>
  gt::cols_hide(agg_group) |>
  gt::cols_label(
    all_included ~ "Countries included in the Index",
    not1_un ~ "UN members not included",
    not2_oth ~ "Other entities not included"
  ) |>
  gt::tab_footnote(
    footnote = paste(
      "Other entities includes countries that are not UN members,",
      "dependent and other territories of other countries, disputed countries",
      "and territories, or those with limited recognition."
    ),
    locations = gt::cells_column_labels(columns = not2_oth)
  ) |>
  gt::sub_missing() |>
  gt::cols_align(align = "left", columns = agg_cat) |>
  gt::cols_width(
    agg_cat ~ gt::pct(40),
    all_included ~ gt::pct(20),
    not1_un ~ gt::pct(20),
    not2_oth ~ gt::pct(20)
  ) |>
  out_table()

```

As shown in @fig-dq_scatter, while closely correlated there is a slightly
non-linear relationship between the data coverage score and the percent of
metrics measures, this is expected since the data coverage score applies a
penalty for a country not having complete data across the measurement framework.

```{r}
#| label: fig-dq_scatter
#| fig-cap: >
#|   Scatter plot of data coverage measures for all countries and territories
#| warning: false
#| dev: ragg_png
ggplot(bipa_dqc$dq_data, aes(x = p_m, y = x_a, colour = dq_grade)) +
  geom_hline(
    yintercept = bipa_dqc$dq_ref$x_a / 2,
    colour = "#999999",
    linetype = "dashed",
    linewidth = 0.5
  ) +
  geom_vline(
    xintercept = 2 / 3,
    colour = "#999999",
    linetype = "dashed",
    linewidth = 0.5
  ) +
  geom_abline(
    slope = 161,
    intercept = 0,
    colour = "#cccccc",
    linewidth = 0.25
  ) +
  geom_point(alpha = 0.5) +
  annotate(
    geom = "label",
    x = 0.01,
    y = 81.5,
    label = expression(Q[c] ~ "= 80.54"),
    colour = "#999999",
    family = "Open Sans",
    size = 3,
    fontface = "italic",
    label.size = 0,
    hjust = 0,
    vjust = 0
  ) +
  annotate(
    geom = "label",
    x = 0.68,
    y = 1,
    label = expression(p[m] ~ "= 66.7%"),
    colour = "#999999",
    family = "Open Sans",
    size = 3,
    fontface = "italic",
    label.size = 0,
    hjust = 0,
    vjust = 0
  ) +
  scale_colour_brewer(
    palette = "Dark2",
    guide = guide_legend(title = "Data coverage\ngrade", position = "bottom")
  ) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = expansion(add = 0.02)
  ) +
  scale_y_continuous(
    limits = c(0, 162),
    expand = expansion(add = 2)
  ) +
  coord_fixed(ratio = 1 / bipa_dqc$dq_ref$x_a) +
  labs(
    y = expression(Data ~ coverage ~ score ~ (Q[c])),
    x = expression(Percent ~ of ~ metrics ~ (p[m])),
    alt = paste(
      "A scatter plot of the percent of total metrics (on the horizontal axis)",
      "against the data coverage score (on the vertical axis),",
      "with point colour varying by data coverage grade."
    )
  ) +
  theme_minimal(base_family = "Open Sans") +
  theme(
    panel.grid.minor = element_blank()
  )

```

There is no statistically significant correlation between a country's overall
score in the Blavatnik Index and either its data coverage score or the percent
of metrics it has data for. However, as @fig-dq_correl shows, there does appear
a relationship between the minimum score for the Blavatnik Index and the
data coverage score[^min_corel], which is likely a function of the data normalisation
process that results in country scores becoming relative measures between 0 and
1.

```{r}
#| label: fig-dq_correl
#| fig-cap: >
#|   Scatter plot of the data coverage score and Blavatnik Index score
#| warning: false
#| dev: ragg_png
dq_index <- bipa_results |>
  dplyr::filter(structure_id == 0) |>
  dplyr::left_join(
    bipa_dqc$dq_data |> dplyr::select(cc_iso3c, x_a, p_m, dq_grade),
    by = "cc_iso3c"
  )

ggplot(dq_index, aes(x = x_a, y = value, colour = dq_grade)) +
  geom_point(alpha = 0.5) +
  scale_colour_brewer(
    palette = "Dark2",
    guide = guide_legend(title = "Data coverage\ngrade", position = "bottom")
  ) +
  scale_x_continuous(
    limits = c(80, 162),
    expand = expansion(add = 2)
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    expand = expansion(add = 0.02)
  ) +
  coord_fixed(ratio = bipa_dqc$dq_ref$x_a / 2) +
  labs(
    x = expression(Data ~ coverage ~ score ~ (Q[c])),
    y = "Blavatnik Index score",
    alt = paste(
      "A scatter plot of data coverage scores (on the horizontal axis)",
      "against Blavatnik Index scores (on the vertical axis),",
      "with point colour varying by data coverage grade."
    )
  ) +
  theme_minimal(base_family = "Open Sans") +
  theme(
    panel.grid.minor = element_blank()
  )
```

:::{.landscape}

```{r}
#| label: tbl-dq_included
#| tbl-cap: >
#|   Data coverage metadata for countries included in the Blavatnik Index of
#|   public administration 2024

dq_all_entities <- cc_meta |>
  dplyr::left_join(
    bipa_dqc$dq_data,
    by = "cc_iso3c"
  ) |>
  dplyr::mutate(
    cc_status = dplyr::case_when(
      grepl("^Other", cc_status) ~ "Other ISO 3166-1 entity",
      grepl("^User", cc_status) ~ "Not an ISO 3166-1 entitty",
      TRUE ~ cc_status
    )
  ) |>
  dplyr::select(
    cc_name_short,
    cc_iso3c,
    cc_status,
    bipa_region,
    income_group,
    dq_grade,
    x_a,
    p_m,
    included
  )

dq_all_entities |>
  dplyr::filter(included) |>
  dplyr::arrange(cc_name_short, .locale = "en_GB") |>
  gt::gt() |>
  gt::cols_hide(included) |>
  gt::cols_label(
    cc_name_short = "Country",
    cc_iso3c = "Code",
    cc_status = "Status",
    bipa_region = "Region",
    income_group = "Income group",
    dq_grade = "Grade",
    x_a = "Score",
    p_m = "% metrics"
  ) |>
  gt::tab_spanner(
    label = "Data coverage",
    columns = c(dq_grade, x_a),
    id = "dq"
  ) |>
  gt::fmt_number(x_a) |>
  gt::fmt_percent(p_m, decimals = 1) |>
  gt::cols_align("center", dq_grade) |>
  gt::tab_options(
    table.width = gt::px(1000),
    container.height = 600,
    latex.use_longtable = TRUE
  ) |>
  out_table()

```

:::

:::{.landscape}

```{r}
#| label: tbl-dq_not_included
#| tbl-cap: >
#|   Data coverage metadata for countries and territories not included in the
#|   Blavatnik Index of public administration 2024

dq_all_entities |>
  dplyr::filter(is.na(included) | !included) |>
  dplyr::arrange(cc_name_short, .locale = "en_GB") |>
  gt::gt() |>
  gt::cols_hide(included) |>
  gt::cols_label(
    cc_name_short = "Country/Territory",
    cc_iso3c = "Code",
    cc_status = "Status",
    bipa_region = "Region",
    income_group = "Income group",
    dq_grade = "Grade",
    x_a = "Score",
    p_m = "% metrics"
  ) |>
  gt::tab_spanner(
    label = "Data coverage",
    columns = c(dq_grade, x_a),
    id = "dq"
  ) |>
  gt::fmt_number(x_a) |>
  gt::fmt_percent(p_m, decimals = 1) |>
  gt::sub_missing() |>
  gt::cols_align("center", dq_grade) |>
  gt::tab_options(
    table.width = gt::px(1000),
    container.height = 600,
    latex.use_longtable = TRUE
  ) |>
  out_table()

```

:::

```{r}
#| label: hkg_dq
#| echo: false
hkg_dq <- bipa_dqc$dq_data |> dplyr::filter(cc_iso3c == "HKG")
```

[^hkg]: Hong Kong appears separately in many of the data sources used to
  calculate the Blavatnik Index and while it was above the thresholds for
  inclusion with a data coverage score of `{r} scales::number(hkg_dq$x_a, 0.01)`
  and `{r} scales::percent(hkg_dq$p_m, 0.1)` of total metrics, it has not been
  included as it is a territory of China rather than a separate national
  entity. As a result in @tbl-dq_grades, Hong Kong has been included in grade
  E, however Hong Kong's underlying data coverage metrics are equivalent to
  other countries classified as grade D.

[^min_corel]: This effect is also apparent when looking at the percent of total metrics.