---
format:
  html:
    subtitle: | 
      How we normalise source data into metrics with a common 0 to 1 score.
source_document: https://index.bsg.ox.ac.uk/posts/rescaling_transformation/
order: 114
---

# Re-scaling and transformation of data {#sec-rescaling_transformation}

As discussed in the section on data aggregation (@sec-data_aggregation), the
metrics for the Blavatnik Index of Public Administration normalised versions
of the source data to re-scale them into the range 0 to 1, where 0 represents
the lowest performance and 1 represents the highest performance of the group
of countries the data relates to. This section provides further details on
the re-scaling and transformation methods used.

For the majority of metrics this re-scaling is a simple min-max normalisation,
however there are 24 metrics which undergo some other form of transformation.

All the re-scaling operations take place after the source data has been limited
to countries identified for inclusion in the Index. Thus, the re-scaled data
represents performance relative to countries included in the Index, it does not
necessarily represent performance relative to all countries that are included
in the original source for that specific metric, nor does it represent the
performance relative to any absolute/theoretical scale limits.

## Min-max normalisation

65 of the 89 metrics are re-scaled using min-max normalisation. This
normalisation converts the minimum value in the observed data to 0 and the
maximum value in the observed data to 1, all other values are re-scaled
accordingly.

The metric value for a given country ($m_c$) is calculated as the difference
between the country’s score in the source data ($x_c$) and the minimum score
($x_{min}$), this difference is then divided by the range of scores in the
source data (difference between the maximum score in the source data,
$x_{max}$, and the minimum score in the source data, $x_{min}$), see
equation 1.

$$
m_c = \frac{(x_c - x_{min})}{(x_{max} - x_{min})} \tag{1}
$$ 

## Inverted min-max normalisation

For 8 metrics their base scaling is such that the highest score represents
worse performance than the lowest score, for these metrics the normalisation
is inverted. This is equivalent to conducting a min-max normalisation above
but subtracting this score from 1, see equation 2.

$$
m_c = 1 - \frac{(x_c - x_{min})}{(x_{max} - x_{min})} \tag{2}
$$

## Distance re-scaling

For 4 metrics their re-scaling is based on their distance from a reference
point. For these metrics both the highest and lowest scoring countries
represent the worst performance and countries closest to the reference point
represent the best performance.

- For the two metrics relating to gender equality the reference point is 50%,
  i.e. the country with the proportion of women in public employment closest to
  50% is the country with the highest performance, and vice versa.
- For the metric relating to the gender pay ratio (the ratio of female to male
  pay in the public sector) the reference point is 1, i.e. the country where
  female pay is closest to male pay is the country with the highest
  performance, and vice versa.
- For the metric on staff turnover in tax administrations the reference point
  is the median value, i.e. both countries with no/very low turnover and
  countries with very high turnover are low performers. For the gender measures
  the reference points can be set conceptually – gender equality implies a
  50:50 split in the composition of staff and equality of pay between men and
  women. However, while high and low turnover are both problematic there is no
  consensus on what an ideal level of turnover should be, therefore the median
  of the observed data is used.

First, for each country its distance ($d_c$) is calculated as the absolute
difference between the country’s score in the source data ($x_c$) from the
reference value ($r$), see equation 3. The distances are then used as the
inputs to the min-max normalisation to calculate the metric value for the
country ($m_c$), see equation 4.

$$
d_c = | x_c - r | \tag{3}
$$ 

$$
m_c = \frac{d_c - d_{min}}{d_{max} - d_{min}} \tag{4}
$$ 

## BTI and SGI re-scaling

The Blavatnik Index of Public Administration makes use of two sources from
the Bertelsmann Stiftung: the Bertelsmann Transformation Index (BTI) and the
Sustainable Governance Indicators (SGI). While these two sources have similar
aims, to assess the quality of governance and achievement of public policy
goals, and use similar methodologies they have different scopes for country
inclusion – the BTI covers countries that were not members of the OECD prior to
1989, while the SGI covers all current OECD and EU members. The SGI was a key
data source in the InCiSE 2019 report, in seeking to expand coverage globally,
for the Blavatnik Index of Public Administration we have paired 5 of the SGI
variables with 5 from the BTI.

153 countries are measured across the two sources: 26 countries are only
included in the SGI, 122 countries are only included in the BTI, while 15
countries are included in both the BTI and the SGI. Both the BTI and SGI both
ask expert assessors to rate countries on a scale of 1 to 10, and while they
have similar aims the questions and intent of the studies is calibrated to the
differing development levels of the different sets of countries included in
each study. @tbl-bti_sgi_mean shows the average scores across the 10 variables
from the BTI and SGI sources split by country coverage, it shows that the 15
countries included in both datasets score higher in the BTI than the other
countries the BTI (6.8 vs 4.8) but in the SGI they score lower than the other
countries in the SGI (5.5 vs 6.8).

```{r}
#| label: tbl-bti_sgi_mean
#| tbl-cap: >
#|   Average scores across the variables from the BTI and SGI data sources by
#|   country inclusion

source("R/out_table.R")

bipa_source <- vroom::vroom(
  file = c(
    "../bipa2024_sourcedata/data_out/bti_2024.csv",
    "../bipa2024_sourcedata/data_out/sgi_2022.csv"
  ),
  show_col_types = FALSE
)

bti_sgi_data <- bipa_source |>
  dplyr::mutate(
    source = dplyr::if_else(grepl("^bti", variable), "bti", "sgi")
  )

bti_sgi_means <- bti_sgi_data |>
  dplyr::summarise(value = mean(value), .by = c(cc_iso3c, source)) |>
  dplyr::add_count(cc_iso3c) |>
  dplyr::mutate(
    group = dplyr::case_when(
      n == 1 & source == "bti" ~ "bti_only",
      n == 1 & source == "sgi" ~ "sgi_only",
      n == 2 ~ "bti_sgi"
    )
  ) |>
  dplyr::summarise(value = mean(value), .by = c(source, group)) |>
  tidyr::pivot_wider(names_from = group, values_from = value)

bti_sgi_means |>
  dplyr::mutate(
    source = dplyr::case_match(
      source,
      "bti" ~ "Bertelsmann Transformation Index (BTI)",
      "sgi" ~ "Sustainable Governance Indicators (SGI)"
    )
  ) |>
  gt::gt() |>
  gt::cols_label(
    source = "Data source",
    bti_only = "Countries only in the BTI",
    bti_sgi = "Countries in both the BTI and SGI",
    sgi_only = "Countries only in the SGI"
  ) |>
  gt::cols_width(
    source ~ gt::pct(40),
    bti_only ~ gt::pct(20),
    bti_sgi ~ gt::pct(20),
    sgi_only ~ gt::pct(20)
  ) |>
  gt::fmt_number(columns = -source, decimals = 1) |>
  gt::sub_missing() |>
  out_table()

```

As implied by the differences in @tbl-bti_sgi_mean, and as shown in
@tbl-bti_sgi_minmax, across the 15 countries included in both sources their
average minimum and maximum scores in the BTI are higher than their average
minimum and maximum scores in the SGI. These results suggest that in combining
these two different sources there should be some form of calibration of their
re-scaling such that data from the SGI is effectively weighted higher than
data from the BTI.

```{r}
#| label: tbl-bti_sgi_minmax
#| tbl-cap: >
#|   Average minimum and maximum scores across the BTI and SGI data sources
#|   for the 15 countries included in both data sources
bti_sgi_minmax <- bti_sgi_data |>
  dplyr::add_count(cc_iso3c) |>
  dplyr::mutate(
    group = dplyr::case_when(
      n == 7 & source == "bti" ~ "bti_only",
      n == 26 & source == "sgi" ~ "sgi_only",
      n == 33 ~ "bti_sgi"
    )
  ) |>
  dplyr::filter(group == "bti_sgi") |>
  dplyr::summarise(
    min = min(value),
    max = max(value),
    .by = c(source, group, variable)
  ) |>
  dplyr::summarise(
    across(c(min, max), mean),
    .by = c(source, group)
  )

bti_sgi_minmax |>
  dplyr::select(-group) |>
  dplyr::mutate(
    source = dplyr::case_match(
      source,
      "bti" ~ "Bertelsmann Transformation Index (BTI)",
      "sgi" ~ "Sustainable Governance Indicators (SGI)"
    )
  ) |>
  gt::gt() |>
  gt::cols_label(
    source = "Data source",
    min = "Mean minimum score",
    max = "Mean maximum score"
  ) |>
  gt::cols_width(
    source ~ gt::pct(40),
    min ~ gt::pct(30),
    max ~ gt::pct(30)
  ) |>
  gt::fmt_number(columns = c(min, max), decimals = 1) |>
  out_table()

```

Based on the minimum and maximum scores shown in @tbl-bti_sgi_minmax, a pragmatic
calibration has been adopted such that re-scaled scores from the BTI using
min-max normalisation have a range of 0.0 to 0.8 (see equation 5) and re-scaled
scores from the SGI using min-max normalisation have a range of 0.3 to 1.0
(equation 6).

BTI normalisation:
$$
m_c = \frac{x_c - x_{min}}{(x_{max} - x_{min}} * 0.8 \tag{5}
$$ 

SGI normalisation:
$$
m_c = \left( \frac{ x_c - x_{min}}{x_{max} - x_{min}} * 0.7 \right) + 0.3 \tag{6}
$$

